---
title: "Baseball Scouting Package Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{baseballscouting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(baseballscouting)
```

## Welcome to `baseballscouting`

The `baseballscouting` package provides tools to explore and analyze baseball data, helping you uncover where certain pitchers and hitters excel—and where they don't. Additionally, the package includes simulation capabilities that allow you to predict outcomes of matchups between pitchers and batters. This dual focus makes `baseballscouting` an excellent toolkit for both baseball enthusiasts and data analysts.

## What can you do with `baseballscouting`?

### Analyze Performance Data

With `baseballscouting`, you can dive deep into baseball statistics to:

- Identify where pitchers are most effective by analyzing their pitch locations and outcomes.
- Discover where hitters perform best by examining their success rates across different pitch types and locations.

By leveraging comprehensive data and powerful visualizations, you can uncover patterns and trends that would otherwise go unnoticed.

#### Example of Analyzing a Hitter with `generate_hitter` Function
```{r}
hitter_ids <- c(668804)  # Bryan Reynolds
start_date <- "2024-01-01"
end_date <- "2024-12-31"
generate_hitter(player_ids = hitter_ids, start_date = start_date, end_date = end_date)
```

The first table shows you the average exit velocity (how fast the ball is hit), average launch angle of the ball, hard hit rate (percentage of percentage of batted balls hit 95 MPH or greater), and strikeout rate (how often a hitter strikes out).

The heatmaps shows you the average exit velocity of batter across different areas of the strike zone. This can give valuable insights into where the hitter struggles and where they excel and give a pitcher a better idea of where to try to pitch them.

#### Example of Analyzing a Hitter with `generate_pitcher` function
```{r}
pitcher_ids <- c(605483)  # Gerrit Cole
start_date <- "2024-01-01"
end_date <- "2024-12-31"
generate_pitcher(player_ids = pitcher_ids, start_date = start_date, end_date = end_date)
```

The first table shows the walk rate (how often pitchers walk batters, given by a proportion of number of walks divided by batters faced) and the strikeout rate (how often a pitcher strikes batters out given by a similar proportion).

The heatmap show how often batters swing and miss at a pitcher's pitches (given by a proportion of number of swings and misses divided by the total number of swings). If a pitcher generates more swings and misses then this is generally a good indicator that their pitches are moving and performing how they want.

### Simulate Matchups

The package's simulation tools allow you to model hypothetical matchups between pitchers and batters. These simulations take into account factors like:

- The pitcher's tendencies, pitch types, and locations.
- The hitter's success rates against different pitches and locations.

For example, you can simulate 1,000 at-bats between a specific pitcher and hitter to predict likely outcomes such as strikeouts, walks, and hits. These insights can be used for strategy, analysis, or just for fun.

#### Example: Simulating an At-Bat

Here’s how you can use `baseballscouting` to simulate matchups between a pitcher and a batter. Let’s see how Gerrit Cole might fare against Mike Trout over a simulated series of at-bats.

```{r}
results <- at_bat_sim(
  pitcher_id = 543037,  # Gerrit Cole
  batter_id = 545361,   # Mike Trout
  start_date = "2022-04-01",
  end_date = "2022-10-01",
  num_simulations = 1000,
  num_cores = 2
)
```

The output data frame contains two columns:

- `Outcome`: The type of event (e.g., strikeout, walk, single, etc.).
- `Probability`: The likelihood of the event occurring, based on the simulation results.

For example:

| Outcome    | Probability |
|------------|-------------|
| strikeout  | 0.23        |
| walk       | 0.08        |
| single     | 0.15        |
| ...        | ...         |

This gives you an analytical view of how the matchup could play out based on the players' historical data.

#### Adjusting Parameters

You can adjust the number of simulations and cores for better performance:

- Increasing `num_simulations` provides more accurate probabilities but takes longer to compute.
- Increasing `num_cores` utilizes more CPU cores for faster computation (useful for large simulations).


### Why `baseballscouting`?

The package combines the thrill of baseball analysis with robust statistical tools, empowering you to:

- Explore key insights about player performance.
- Simulate realistic game scenarios.
- Make data-driven decisions or simply enjoy a deeper understanding of the sport.

### Notes

1. Ensure that the pitcher and batter IDs are valid Statcast IDs.
2. Parallel processing (`num_cores`) may require additional setup on some systems (e.g., Windows).

## Get Started

To begin, install the package (code below) and start exploring! Here are some additional resources to guide you:

``` r
devtools::install_github("braeden-falzarano/baseballscouting")
```

- [Find a Player's ID Here](https://www.smartfantasybaseball.com/tools/)
- [Learn More About Advanced Stats Here](https://www.mlb.com/glossary/advanced-stats)
- [Explore the Full Repository](https://github.com/braeden-falzarano/baseballscouting/)

We’re excited to see what insights you uncover with `baseballscouting`!
